%________________________________________________________________________________________
% @brief    LaTeX2e Resume for William Scott
\documentclass[margin,line]{resume}
\usepackage[usenames]{color}
\definecolor{mySideColor}{rgb}{0.5,0.5,0.5}
\linespread{1.1}
%________________________________________________________________________________________
\begin{document}
\name{\huge William Scott}
\begin{resume}
\vspace{-4mm}

  % ==========================
  % Contact Information
  % ==========================

  \section{\mysidestyle \textcolor{mySideColor}{Contact}}

  http://williamscott.me \hfill wds@williamscott.me

%  Address 1 \hfill Phone \\
%  Address 2 \hfill wds@williamscott.me


  % ==========================
  % Summary / Objective
  % ==========================

  \section{\mysidestyle \textcolor{mySideColor}{Summary}}

William Scott is a software engineer with experience in web and mobile
application development who thrives in a fast-paced environment. He is skilled
in the entire product life cycle, including feature planning, team management,
implementation, and product support. William is passionate about thinking
creatively and developing solutions to real-world problems.

  % ==========================
  % Skills
  % ==========================

  \section{\mysidestyle \textcolor{mySideColor}{Skills}}

  \textbf{Languages:} Java, Scala, JavaScript, Objective-C, Python, Ruby, SQL
	\vspace{-2mm}

  \textbf{Technologies:} AngularJS, Node.js, iOS, MongoDB, Git, PostgreSQL, JavaEE, Android, jQuery, Spring, Tomcat, Maven, JUnit, Jenkins, Heroku, Amazon Web Services, J2EE
	\vspace{-2mm}

  \textbf{Methodologies:} RESTful Web Services, Continuous Integration, MVC, Unit Testing, Design Patterns, Agile / Scrum, Object-Oriented Design
	\vspace{-2mm}

  % ==========================
  % Experience
  % ==========================

  \section{\mysidestyle \textcolor{mySideColor}{Experience}}

  \textbf{Wireless Generation}, Durham, NC \hfill Jan 2012 - Present\vspace{1mm}\\
  \textsl{Senior Software Engineer}\\
  \vspace{-3mm}
  \begin{list2}
\item Developed an education data store and application platform, with full-stack
  involvement and specific responsibility in the data store, data access layer,
  and secure RESTful API. (Java, Spring, JAX-RS)
\item Led the design and implementation of MongoDB sharding and indexing strategy
  and employed profiling and code analysis to optimize queries. (MongoDB,
  JavaScript, Python)
\item Constructed initial API documentation generation workflow and worked closely
  with the technical writer team to deliver platform documentation. (Python,
  Bash)
\item Ensured platform quality via full-stack unit and integration tests. (JUnit,
  Ruby)
\item Developed collaborative tabled-based applications which aided teachers
  with integrated curriculum instruction and assessment workflows. (iOS,
  Node.js, JavaScript, HTML5, CSS, Socket.io)
\item Initiated improvements in company culture by mentoring junior engineers and
  advancing workflows with respect to CI, version control, and tooling (Git,
  Jenkins)
  \end{list2}

  \textbf{itMD}, Remote \hfill Apr 2011 - Dec 2011\vspace{1mm}\\
  \textsl{Software Engineer}\\
  \vspace{-3mm}
  \begin{list2}
\item Developed a scalable, highly-available web-based medical imaging network with
  workflows designed specifically for radiologists. (Java, HTML, CSS,
  JavaScript)
\item Designed and implemented a plugin system capable of launching most web-based
  and desktop medical image viewers. (Java)
\item Managed cloud infrastructure, including setup, administration, and
  monitoring, on Amazon Web Services and OpSource as well as private server
  installs. (Bash, Nagios)
\item Collaborated with physicians and radiologists to design, mock-up, and
  document new application features and directed overseas developers.
\item Provided technical customer support to diagnose problems and identify
  application bugs. (Zendesk)
  \end{list2}

  \textbf{Wake Forest University Health Sciences}, Winston-Salem, NC \hfill Nov 2009 - May 2011\vspace{1mm}\\
  \textsl{Analyst / Programmer}\\
  \vspace{-3mm}
  \begin{list2}
\item Developed a secure, patient-driven medical image sharing network as part of
  an NIH-funded project, with specific focus on rural providers and limited
  IT resources.
\item Incorporated HL7 and XDS health care profile functionality. (Java)
\item Produced a clinical imaging workstation which reduced patient CD image import
  errors by 90\%. (Java, Bash)
\item Augmented the open source project dcm4chee-Archive with a custom API and
  event callback system to aid in image transfer between facilities. (Java)
\item Improved performance of RSNA's MIRC software for in-house use by modifying
  image workflow and caching. (Java)
\item Initial member of WFU Mobile Application Development Group which seeks to
  explore and initiate the use of mobile devices in health care. (Android)
  \end{list2}

  \textbf{GreatWall Systems, Inc.}, Winston-Salem, NC \hfill Oct 2007 - Mar 2009\vspace{1mm}\\
  \textsl{Software Engineer}\\
  \vspace{-3mm}
  \begin{list2}
\item Developed multi-core, high-performance parallel firewall solutions working
  with a geographically distributed team.
\item Implemented access rule storage structures and dependency tests. (C++)
\item Analyzed and implemented thread-safe rule order optimization algorithms.
\item Designed and developed a packet session tracking system capable of real-time
  performance.
\item Prepared RFC-compliant firewall benchmarking and testing procedures.
  \end{list2}

  \textbf{Roanoke College Information Services}, Roanoke, VA \hfill May 2003 - Feb 2004\vspace{1mm}\\
  \textsl{Web Programmer}\\
  \vspace{-3mm}
  \begin{list2}
\item Performed initial roll-out of the Roanoke College Web Portal (MyRC).
\item Maintained Linux development and production environments with respect to
  the Java J2EE platform, Tomcat, and MySQL.
\item Developed Java Servlets and ServerPages to provide content and single-on
  functionality for existing web services.
  \end{list2}


  % ==========================
  % Education
  % ==========================

  \section{\mysidestyle \textcolor{mySideColor}{Education}}

  \textbf{Wake Forest University}\vspace{2mm} \hfill Aug 2005 -- May 2007\\
  \textsl{Master of Science}, Computer Science\vspace{-1mm}

  \textbf{Roanoke College}\vspace{2mm} \hfill Aug 2001 -- May 2005\\
  \textsl{Bachelor of Science}, Computer Science \& Mathematics\vspace{-1mm}

  % ==========================
  % Research
  % ==========================

  \section{\mysidestyle \textcolor{mySideColor}{Research}}

  \textbf{Bioinformatics} \hfill Jan 2006 - Dec 2006 \vspace{2mm}\\
  Employed parallel search and clustering algorithms to search protein
  structure databases and infer undocumented protein function using
  3-dimensional profiles of protein active sites.

  \textbf{Graph Theory} \hfill May 2004 - Aug 2004 \vspace{2mm}\\
  Implemented parallel search algorithms on a Beowulf MPI cluster to
  determine optimal frequency assignments for different cellular
  network topologies, which guided a more general proof of such
  assignments.


  % ==========================
  % Activities
  % ==========================

  \section{\mysidestyle \textcolor{mySideColor}{Activities}}

  Recent independent coursework: Advanced iOS Programming (Big Nerd Ranch),
Functional Programming Principles in Scala (Coursera).

  Attend community meetups: TriJUG, Triangle JavaScript, Triangle Cocoa, TriAngular.js,
FullSteam Ahead! Run Club.

  Running: Regularly log 35 miles per week. Completed seven marathons.\vspace{-2mm}

  Pi Kappa Alpha: National Greek Social Fraternity. Elected chapter
  Internal Vice President. Developed and maintained chapter
  website.\vspace{-2mm}

  Upsilon Pi Epsilon: National Computer Science Honors Society.\vspace{-2mm}

\end{resume}
\end{document}
